---
title: "BoS Data"
author: "Jill MacKay"
date: "24 April 2019"
output: html_document
---


# About
If you use JISC online surveys (formerly Bristol Online Surveys) you will have a really consistent file format to deal with. Here's how I deal with mine. 


## Intro to BoS Data
There are two videos about BoS:
* [Creating a Survey in BoS](https://media.ed.ac.uk/media/1_0fss9mxx)
* [Exporting data to Excel](https://media.ed.ac.uk/media/1_091u2uy0)

(We'll be using the same data)



# The R Environment

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(likert)
library(janitor)

```



# Basic import

```{r}
dat <- read_excel("data/results-for-bosdata-2019-04-24-1526.xlsx")

dat <- dat %>% 
  clean_names()

head(dat)

```


# Splitting multiple selection questions

```{r}

wide_dat <- dat %>% 
  separate(col = crisps, sep = ",",
           into = paste0("crisp_",(1:(dat$crisps %>%
                                           str_split(",") %>%
                                           lapply(function(z) length(z)) %>%
                                           unlist() %>%
                                           max()
           ))))


head(wide_dat)
  

```


# Recoding data for likert package

```{r}


```


